Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2022-01-06 analysis/paper/paper.Rmd
cleaning paper code up; updated impact scenarios to include p_chnk; more work to do

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(lubridate)
library(tidytable)
library(janitor)
library(purrr)
library(here)
library(FSA)
library(knitr)
library(kableExtra)
library(stringi)
library(english)
library(lemon)
library(gridExtra)

@@

<!-- In the end, sampling dates were as follows: fall 2019 (mark = November 12-14; recapture = November 19-21), fall 2020 (mark = October 20-23; recapture = October 27-30); spring 2021 (mark = May 18-21). -->

@@

# focus on pikeminnow, to be used for mark-recap models
cmr_df = raw_df %>%
  filter(count > 0) %>%
  # pull out only Northern Pikeminnow
  filter(species == "Northern Pikeminnow") %>%
  mutate(mark_release = if_else(fish_status == "Live" &
                                  capture_type == "Mark",
                                T, F),
         recap = if_else(capture_type == "Recapture",
                         T, F))

@@

```{r effort, eval = T}
effort_df = raw_df %>%
  select(event_name,
         site,
         date,
         crew,
         crew_count,
         method,
         equipment,
         start_time:total_effort,
         total_day_effort) %>%
  distinct() %>%
  filter(method == "Angling") %>%
  mutate(across(total_effort,
                ~ . * crew_count)) %>%
  rename(total_effort_min = total_effort) %>%
  group_by(event_name,
           date) %>%
  summarise(across(c(total_effort_min,
                     crew_count),
                   sum),
            .groups = "drop")

# What size (mm) is considered a large pikeminnow?
large_size = 228

# catch per unit effort
cpue_df = effort_df %>%
  # add back in the number of pikeminnow caught
  left_join(cmr_df %>%
              group_by(event_name, species, date) %>%
              summarise(n_fish = n(),
                        n_large_fish = sum(length >= large_size,
                                           na.rm = T),
                        .groups = "drop")) %>%
  # calculate CPUE a few different ways
  mutate(catch_per_min = n_fish / total_effort_min,
         catch_per_hr  = n_fish / (total_effort_min / 60),
         catch_per_angler_day = n_fish / crew_count,
         catch_lg_per_angler_day = n_large_fish / crew_count)

@@

# Lincoln-Peterson Model
LP_mod = cmr_df %>%
  # filter out spring 2021 (no recapture)
  filter(event_name != "Spring_2021") %>%
  group_by(event_name, species) %>%
  summarise(M = sum(cap_period == "Mark" & fish_status == "Live", na.rm = T),
            n = sum(cap_period == "Recapture"),
            m = sum(cap_period == "Recapture" & capture_type == "Recapture", na.rm = T),
            .groups = "drop") %>%
  nest(data = -c(event_name, species)) %>%
  crossing(model = c("Petersen",
                     "Chapman")) %>%
  mutate(mr_model = map2(data,
                       model,
                      .f = function(x, y) {
                        with(x,
                             FSA::mrClosed(M = M,
                                          n = n,
                                          m = m,
                                          method = y))
                        }),
         N_summ = map(mr_model,
                      .f = summary,
                      incl.SE = T),
         CI = map(mr_model,
                  .f = confint)) %>%
  mutate(N = map_dbl(N_summ,
                     .f = function(x) x[1]),
         SE = map_dbl(N_summ,
                      .f = function(x) x[2]),
         Lci = map_dbl(CI,
                         .f = function(x) x[1]),
         Uci = map_dbl(CI,
                         .f = function(x) x[2])) %>%
  select(-N_summ, -CI)

@@

```{r spring-abund}
total_cpue = cpue_df %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  group_by(species,
           event_name) %>%
  summarise(across(c(total_effort_min,
                     n_fish,
                     n_large_fish,
                     angler_days = crew_count),
                   sum),
            .groups = "drop") %>%
  mutate(catch_per_min = n_fish / total_effort_min,
         catch_per_hr = n_fish / (total_effort_min / 60),
         catch_per_angler_day = n_fish / angler_days,
         catch_lg_per_angler_day = n_large_fish / angler_days)

spring_abund = all_est %>%
  filter(model == "Schnabel") %>%
  select(-range, -prop_range) %>%
  inner_join(total_cpue,
             by = c("event_name", "species")) %>%
  select(species,
         model,
         model_event = event_name,
         N_F = N,
         Lci_F = Lci,
         Uci_F = Uci,
         cpue_F = catch_per_hr) %>%
  group_by(species, model) %>%
  summarise(across(c(N_F:cpue_F),
                   mean),
            .groups = "drop") %>%
  full_join(total_cpue %>%
              filter(str_detect(event_name, "Spring")) %>%
              select(species,
                     cpue_S = catch_per_hr),
            by = "species") %>%
  mutate(N_S = N_F * (cpue_S / cpue_F),
         Lci_S = Lci_F * (cpue_S / cpue_F),
         Uci_S = Uci_F * (cpue_S / cpue_F))

@@

```{r psd}
s_size = 250
q_size = 380

psd_df = cmr_df %>%
  select(species, count, length, recap, event_name) %>%
  filter(recap  != TRUE)

@@

```{r gastric-data}
gastric_df = raw_df %>%
  select(event_name, date, species, method, lavage_id, length, stomach_contents, comments, stomach_contents_weight,                             fish_content_weight) %>%
  mutate(bin_50 = lencat(length, w = 50)) %>%
  filter(species == "Northern Pikeminnow") %>%
  mutate(non_fish_wt = stomach_contents_weight - fish_content_weight) %>%
  mutate(lavaged = case_when(
    is.na(lavage_id) & is.na(stomach_contents) ~ FALSE,
    stomach_contents == "Did Not Lavage" ~ FALSE,
    stomach_contents == "Lost sample CG27-001" ~ FALSE,
    TRUE ~ TRUE
  )) %>%
  mutate(had_contents = case_when(
    lavaged == FALSE ~ FALSE,
    is.na(stomach_contents) ~ FALSE,
    stomach_contents == "Empty" ~ FALSE,
    TRUE ~ TRUE
  )) %>%
  mutate(had_fish_contents = case_when(
    fish_content_weight > 0 ~ TRUE,
    stomach_contents == "MacroInvert-other/Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish-Unk (fish bone/cartilage)" ~ TRUE,
    stomach_contents == "MacroInvert-other/Mountain Whitefish" ~ TRUE,
    stomach_contents == "MacroInvert-other/Algae/Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish -Shiner" ~ TRUE,
    stomach_contents == "Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish Unk" ~ TRUE,
    stomach_contents == "Detritus/Fish -Shiner" ~ TRUE,
    stomach_contents == "MacroInvert-other/Fish-Unk" ~ TRUE,
    stomach_contents == "MacroInvert-other/Detritus/Fish -Shiner" ~ TRUE,
    stomach_contents == "Fish-Unk" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Detritus/Fish-Unk/Other"  ~ TRUE,
    stomach_contents == "Aquatic Veg/Fish-Sucker"  ~ TRUE,
    stomach_contents == "MacroInvert-Worm/Fish-RedsideShiner"  ~ TRUE,
    stomach_contents == "Aquatic Veg/Detritus/Fish-RedsideShiner"  ~ TRUE,
    stomach_contents == "MacroInvert-Other/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish-Sucker/Other" ~ TRUE,
    stomach_contents == "Fish-Unk/Other" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Aquatic Veg/Detritus/Fish-Sucker" ~ TRUE,
    stomach_contents == "Fish-RedsideShiner" ~ TRUE,
    stomach_contents == "Fish-Chinook/Other" ~ TRUE,
    stomach_contents == "Detritus/Fish-RedsideShiner/Other" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Aquatic Veg/Detritus/Fish-RedsideShiner" ~ TRUE,
    stomach_contents == "Detritus/Fish-Sucker/Other" ~ TRUE,
    stomach_contents == "Invertebrates;FishParts"  ~ TRUE,
    stomach_contents == "Invertebrates;Detritus;FishParts;IntestinalWorms"  ~ TRUE,
    stomach_contents == "FishParts"  ~ TRUE,
    stomach_contents == "FishParts;IntestinalWorms"  ~ TRUE,
    TRUE ~ FALSE
  )) %>%
  mutate(had_chinook = case_when(
    stomach_contents == "Fish-Chinook/Other" ~ TRUE,
    TRUE ~ FALSE
  ))

@@

stmch_df = gastric_df %>%
  filter(stomach_contents_weight > 0) %>%
  select(event_name,
         date,
         length,
         stomach_contents_weight,
         fish_content_weight,
         non_fish_wt) %>%
  mutate(p_fish = fish_content_weight / stomach_contents_weight)

psd_df = gastric_df %>%
  group_by(bin_50) %>%
  summarize(n = n())

@@

```{r shoup-temp-data, eval = F}
shoup_temp_df = read_tsv(here("analysis/data/raw_data/USGS_13307000_Salmon_River_Nr_Shoup.txt"),
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

@@

# compile fall results
fall_results = fall_f10 %>%
  select(date, temperature_c, cum_cons_fish_g) %>%
  rename(f10_g = cum_cons_fish_g) %>%
  mutate(f20_g = fall_f20$cum_cons_fish_g,
         f30_g = fall_f30$cum_cons_fish_g,
         f40_g = fall_f40$cum_cons_fish_g,
         f50_g = fall_f50$cum_cons_fish_g,
         f60_g = fall_f60$cum_cons_fish_g,
         f70_g = fall_f70$cum_cons_fish_g,
         f80_g = fall_f80$cum_cons_fish_g,
         f90_g = fall_f90$cum_cons_fish_g) %>%
  mutate( across(contains('_g'),
                 .fns = list(n = ~./avg_DSR_g),
                 .names = "{col}_{fn}") )

fall_g_summ = fall_results %>%
  select(f10_g:f90_g) %>%
  pivot_longer(f10_g:f90_g) %>%
  group_by(name) %>%
  summarize(cumm_g = max(value))

rm(fall_f10, fall_f20, fall_f30, fall_f40, fall_f50, fall_f60, fall_f70, fall_f80, fall_f90)

# compile spring results
spring_results = spring_f10 %>%
  select(date, temperature_c, cum_cons_fish_g) %>%
  rename(f10_g = cum_cons_fish_g) %>%
  mutate(f20_g = spring_f20$cum_cons_fish_g,
         f30_g = spring_f30$cum_cons_fish_g,
         f40_g = spring_f40$cum_cons_fish_g,
         f50_g = spring_f50$cum_cons_fish_g,
         f60_g = spring_f60$cum_cons_fish_g,
         f70_g = spring_f70$cum_cons_fish_g,
         f80_g = spring_f80$cum_cons_fish_g,
         f90_g = spring_f90$cum_cons_fish_g) %>%
  mutate( across(contains('_g'),
                 .fns = list(n = ~./avg_NRR_g),
                 .names = "{col}_{fn}") )

spring_g_summ = spring_results %>%
  select(f10_g:f90_g) %>%
  pivot_longer(f10_g:f90_g) %>%
  group_by(name) %>%
  summarize(cumm_g = max(value))

rm(spring_f10, spring_f20, spring_f30, spring_f40, spring_f50, spring_f60, spring_f70, spring_f80, spring_f90)

@@

# summarize potential Chinook eaten for each time period by one pikeminnow
adult_impact = fall_results %>%
  summarise(across(ends_with("g_n"), max)) %>%
  add_column(season = "Fall",
             .before = 0) %>%
  bind_rows(spring_results %>%
              summarise(across(ends_with("g_n"), max)) %>%
              add_column(season = "Spring",
                         .before = 0)) %>%
  pivot_longer(cols = ends_with("g_n"),
               names_to = "perc_diet",
               values_to = "juv_chnk") %>%
  mutate(across(perc_diet,
                str_extract,
                "[:digit:]+"),
         across(perc_diet,
                as.integer)) %>%
  left_join(spring_abund %>%
              select(N_F:Uci_F,
                     N_S:Uci_S) %>%
              pivot_longer(everything()) %>%
              mutate(season = if_else(str_detect(name, "_F$"),
                                      "Fall",
                                      "Spring")) %>%
              mutate(across(name,
                            str_remove,
                            "_F$"),
                     across(name,
                            str_remove,
                            "_S$")) %>%
              pivot_wider(names_from = name,
                          values_from = value)) %>%
  mutate(smolt_N = N * juv_chnk,
         smolt_Lci = Lci * juv_chnk,
         smolt_Uci = Uci * juv_chnk) %>%
  bind_cols(sar) %>%
  mutate(adult_N = smolt_N * medsar,
         adult_Lci = smolt_Lci * qnorm(0.025, medsar, sdsar),
         adult_Uci = smolt_Uci * qnorm(0.975, medsar, sdsar))

# sum fall and spring impacts
total_impacts = adult_impact %>%
  group_by(perc_diet) %>%
  summarise(across(c(ends_with("_N"),
                     ends_with("_Lci"),
                     ends_with("_Uci")),
                   sum))

>>>>

```{r load-libraries}
library(tidyverse)
library(magrittr)
library(janitor)
library(here)
library(lubridate)
library(FSA)
library(english)
library(lubridate)
library(tidytable)
# library(purrr)
# library(knitr)
# library(kableExtra)
# library(stringi)

# library(lemon)
# library(gridExtra)

@@

@@

# capture/mark/recpature data frame; focus on pikeminnow, to be used for mark-recap models
cmr_df = raw_df %>%
  filter(count > 0) %>%                                     # filter out effort-only records
  filter(species == "Northern Pikeminnow") %>%              # focus on NPM
  filter(method == "Angling") %>%
  select(event_name, 
         date,
         method, 
         species, 
         count, 
         length, 
         fish_status, 
         capture_type) %>%
  # if fish_status = Live & capture_type = Mark, set as mark_release as TRUE
  # if capture_type = Recapture, set recap to TRUE
  mutate(mark_release = if_else(fish_status == "Live" &     
                                capture_type == "Mark",
                                T, F),
         recap = if_else(capture_type == "Recapture",
                         T, F))

@@

```{r effort, eval = T}
# What size (mm) is considered a large pikeminnow?
large_size = 380

# catch per unit effort
cpue_df = raw_df %>%
  select(event_name,
         site,
         date,
         crew,
         crew_count,
         method,
         equipment,
         start_time:total_effort,
         total_day_effort) %>%
  distinct() %>%
  filter(method == "Angling") %>%
  mutate(across(total_effort,
                ~ . * crew_count)) %>%
  rename(total_effort_min = total_effort) %>%
  group_by(event_name,
           date) %>%
  summarise(across(c(total_effort_min,
                     crew_count),
                   sum),
            .groups = "drop") %>%
    left_join(cmr_df %>%
              group_by(event_name, species, date) %>%
              summarise(n_fish = n(),
                        n_large_fish = sum(length >= large_size,
                                           na.rm = T),
                        .groups = "drop")) %>%
  mutate(catch_per_hr = n_fish / (total_effort_min / 60),
         catch_per_angler_day = n_fish / crew_count,
         catch_lg_per_angler_day = n_large_fish / crew_count)

@@

# Lincoln-Peterson Model
LP_mod = cmr_df %>%
  filter(event_name != "Spring_2021") %>%
  group_by(event_name, species) %>%
  summarise(M = sum(cap_period == "Mark" & fish_status == "Live", na.rm = T),
            n = sum(cap_period == "Recapture"),
            m = sum(cap_period == "Recapture" & capture_type == "Recapture", na.rm = T),
            .groups = "drop") %>%
  nest(data = -c(event_name, species)) %>%
  crossing(model = c("Petersen",
                     "Chapman")) %>%
    mutate(mr_model = map2(data,
                       model,
                      .f = function(x, y) {
                        with(x,
                             FSA::mrClosed(M = M,
                                          n = n,
                                          m = m,
                                          method = y))
                        }),
         N_summ = map(mr_model,
                      .f = summary,
                      incl.SE = T),
         CI = map(mr_model,
                  .f = confint)) %>%
    mutate(N = map_dbl(N_summ,
                     .f = function(x) x[1]),
         SE = map_dbl(N_summ,
                      .f = function(x) x[2]),
         Lci = map_dbl(CI,
                         .f = function(x) x[1]),
         Uci = map_dbl(CI,
                         .f = function(x) x[2])) %>%
    select(-N_summ, -CI)

@@

```{r spring-abund}
total_cpue = cpue_df %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  group_by(species,
           event_name) %>%
  summarise(across(c(total_effort_min,
                     n_fish,
                     n_large_fish,
                     angler_days = crew_count),
                   sum),
            .groups = "drop") %>%
  mutate(catch_per_hr = n_fish / (total_effort_min / 60),
         catch_per_angler_day = n_fish / angler_days,
         catch_lg_per_angler_day = n_large_fish / angler_days)

spring_abund = all_est %>%
  filter(model == "Schnabel") %>%
  select(-range, -prop_range) %>%
  inner_join(total_cpue,
             by = c("event_name", "species")) %>%
  select(species,
         model,
         model_event = event_name,
         N_F = N,
         Lci_F = Lci,
         Uci_F = Uci,
         cpue_F = catch_per_hr) %>%
  group_by(species, model) %>%
  summarise(across(c(N_F:cpue_F),
                   mean),
            .groups = "drop") %>%
    full_join(total_cpue %>%
              filter(str_detect(event_name, "Spring")) %>%
              select(species,
                     cpue_S = catch_per_hr),
            by = "species") %>%
  # calculate spring abundance estimate
  mutate(N_S = N_F * (cpue_S / cpue_F),
         Lci_S = Lci_F * (cpue_S / cpue_F),
         Uci_S = Uci_F * (cpue_S / cpue_F))

@@

```{r psd}
s_size = 250        # stock size
q_size = large_size # quality size

psd_df = cmr_df %>%
  select(event_name,
         species,
         count,
         length,
         recap) %>%
  filter(recap != T)

@@

```{r gastric-data}
gastric_df = raw_df %>%
  select(event_name, 
         date, 
         species,
         method,
         length,
         lavage_id,
         stomach_contents,
         stomach_contents_weight,
         fish_content_weight,
         comments) %>%
  #mutate(bin_50 = lencat(length, w = 50)) %>%
  filter(species == "Northern Pikeminnow",
         method == "Angling") %>%
  mutate(non_fish_wt = stomach_contents_weight - fish_content_weight) %>%
  mutate(lavaged = case_when(
    is.na(lavage_id) & is.na(stomach_contents) ~ FALSE,
    stomach_contents == "Did Not Lavage" ~ FALSE,
    stomach_contents == "Lost sample CG27-001" ~ FALSE,
    TRUE ~ TRUE
  )) %>%
  mutate(had_contents = case_when(
    lavaged == FALSE ~ FALSE,
    is.na(stomach_contents) ~ FALSE,
    stomach_contents == "Empty" ~ FALSE,
    TRUE ~ TRUE
  )) %>%
  mutate(had_fish_contents = case_when(
    fish_content_weight > 0 ~ TRUE,
    stomach_contents == "MacroInvert-other/Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish-Unk (fish bone/cartilage)" ~ TRUE,
    stomach_contents == "MacroInvert-other/Mountain Whitefish" ~ TRUE,
    stomach_contents == "MacroInvert-other/Algae/Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish -Shiner" ~ TRUE,
    stomach_contents == "Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish Unk" ~ TRUE,
    stomach_contents == "Detritus/Fish -Shiner" ~ TRUE,
    stomach_contents == "MacroInvert-other/Fish-Unk" ~ TRUE,
    stomach_contents == "MacroInvert-other/Detritus/Fish -Shiner" ~ TRUE,
    stomach_contents == "Fish-Unk" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Detritus/Fish-Unk" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Detritus/Fish-Unk/Other"  ~ TRUE,
    stomach_contents == "Aquatic Veg/Fish-Sucker"  ~ TRUE,
    stomach_contents == "MacroInvert-Worm/Fish-RedsideShiner"  ~ TRUE,
    stomach_contents == "Aquatic Veg/Detritus/Fish-RedsideShiner"  ~ TRUE,
    stomach_contents == "MacroInvert-Other/Fish-Unk" ~ TRUE,
    stomach_contents == "Fish-Sucker/Other" ~ TRUE,
    stomach_contents == "Fish-Unk/Other" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Aquatic Veg/Detritus/Fish-Sucker" ~ TRUE,
    stomach_contents == "Fish-RedsideShiner" ~ TRUE,
    stomach_contents == "Fish-Chinook/Other" ~ TRUE,
    stomach_contents == "Detritus/Fish-RedsideShiner/Other" ~ TRUE,
    stomach_contents == "MacroInvert-Other/Aquatic Veg/Detritus/Fish-RedsideShiner" ~ TRUE,
    stomach_contents == "Detritus/Fish-Sucker/Other" ~ TRUE,
    stomach_contents == "Invertebrates;FishParts"  ~ TRUE,
    stomach_contents == "Invertebrates;Detritus;FishParts;IntestinalWorms"  ~ TRUE,
    stomach_contents == "FishParts"  ~ TRUE,
    stomach_contents == "FishParts;IntestinalWorms"  ~ TRUE,
    TRUE ~ FALSE
  )) %>%
  mutate(had_chinook = case_when(
    stomach_contents == "Fish-Chinook/Other" ~ TRUE,
    TRUE ~ FALSE
  )) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " ")))

@@

stmch_df = gastric_df %>%
  select(event_name,
         species,
         date,
         length,
         stomach_contents_weight,
         fish_content_weight,
         non_fish_wt) %>%
  filter(stomach_contents_weight > 0) %>%
  mutate(p_fish = fish_content_weight / stomach_contents_weight)

# psd_df = gastric_df %>%
#   group_by(bin_50) %>%
#   summarize(n = n())

@@

```{r shoup-temp-data, eval = F}
shoup_temp_df = read_tsv(here("analysis/data/raw_data/USGS_13307000_Salmon_River_Nr_Shoup.txt"),
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`) %>%
  select(datetime, water_temp_c) %>%
  mutate(month = month(datetime),
         day = day(datetime)) %>%
  group_by(month, 
           day) %>%
  summarize(mean_water_temp = mean(water_temp_c, na.rm = T))

@@

# compile fall results
fall_results = fall_f10 %>%
  select(date, temperature_c, cum_cons_fish_g) %>%
  rename(f10_g = cum_cons_fish_g) %>%
  mutate(f20_g = fall_f20$cum_cons_fish_g,
         f30_g = fall_f30$cum_cons_fish_g,
         f40_g = fall_f40$cum_cons_fish_g,
         f50_g = fall_f50$cum_cons_fish_g,
         f60_g = fall_f60$cum_cons_fish_g,
         f70_g = fall_f70$cum_cons_fish_g,
         f80_g = fall_f80$cum_cons_fish_g,
         f90_g = fall_f90$cum_cons_fish_g) %>%
  mutate(season = "Fall") #%>%
  # mutate( across(contains('_g'),
  #                .fns = list(n = ~./avg_DSR_g),
  #                .names = "{col}_{fn}") )

# compile spring results
spring_results = spring_f10 %>%
  select(date, temperature_c, cum_cons_fish_g) %>%
  rename(f10_g = cum_cons_fish_g) %>%
  mutate(f20_g = spring_f20$cum_cons_fish_g,
         f30_g = spring_f30$cum_cons_fish_g,
         f40_g = spring_f40$cum_cons_fish_g,
         f50_g = spring_f50$cum_cons_fish_g,
         f60_g = spring_f60$cum_cons_fish_g,
         f70_g = spring_f70$cum_cons_fish_g,
         f80_g = spring_f80$cum_cons_fish_g,
         f90_g = spring_f90$cum_cons_fish_g) %>%
  mutate(season = "Spring") # %>%
  # mutate( across(contains('_g'),
  #                .fns = list(n = ~./avg_NRR_g),
  #                .names = "{col}_{fn}") )

bio_results = rbind(fall_results, spring_results)
bio_g_summ = bio_results %>%
  select(season, f10_g:f90_g) %>%
  pivot_longer(f10_g:f90_g) %>%
  group_by(season, name) %>%
  summarize(cumm_g = max(value))

rm(fall_results,
   fall_f10, 
   fall_f20, 
   fall_f30, 
   fall_f40, 
   fall_f50, 
   fall_f60, 
   fall_f70, 
   fall_f80, 
   fall_f90,
   spring_results,
   spring_f10, 
   spring_f20, 
   spring_f30, 
   spring_f40, 
   spring_f50, 
   spring_f60, 
   spring_f70, 
   spring_f80, 
   spring_f90)

@@

# summarize potential Chinook eaten for each time period by one pikeminnow
impact_df = bio_results %>%
  group_by(season) %>%
  summarize(across(ends_with("_g"), max)) %>%
  pivot_longer(cols = ends_with("_g"),
               names_to = "perc_diet",
               values_to = "g_fish_cons") %>%
  mutate(across(perc_diet,
                str_extract,
                "[:digit:]+"),
         across(perc_diet,
                as.integer)) %>%
  crossing(p_chnk = c(.01, .10, .30, .50)) %>%
  mutate(g_chnk = g_fish_cons * p_chnk) %>%
  mutate(n_chnk = ifelse(season == "Fall",
                         g_chnk / avg_DSR_g,
                         g_chnk / avg_NRR_g)) %>%
  left_join(spring_abund %>%
            select(N_F:Uci_F,
                   N_S:Uci_S) %>%
            pivot_longer(everything()) %>%
            mutate(season = if_else(str_detect(name, "_F$"),
                                    "Fall",
                                    "Spring")) %>%
            mutate(across(name,
                          str_remove,
                          "_F$"),
                    across(name,
                           str_remove,
                           "_S$")) %>%
            pivot_wider(names_from = name,
                        values_from = value)) %>%
  mutate(juv_N = N * n_chnk,
         juv_Lci = Lci * n_chnk,
         juv_Uci = Uci * n_chnk) %>%
  bind_cols(sar) %>%
  mutate(adult_N = juv_N * medsar,
         adult_Lci = juv_Lci * qnorm(0.025, medsar, sdsar),
         adult_Uci = juv_Uci * qnorm(0.975, medsar, sdsar))

# sum fall and spring impacts
total_impacts = impact_df %>%
  group_by(perc_diet, p_chnk) %>%
  summarise(across(c(ends_with("_N"),
                     ends_with("_Lci"),
                     ends_with("_Uci")),
                   sum),
            .groups = "drop")
